FinalManuscript_DISCS_UG

### 2018-06-26 parts/02_relatedliterature.tex
Edited RRL

Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}. Even the classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.

However, there exists a \textit{fully homomorphic} cryptosystem, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}.

A recent survey of homomorphic encryption by Sen shows that the open problems in the area deal with fully homomorphic encryption, of which the main concern is the speed of such implementations \cite{sen_homomorphic_2013}.

@@

There has been work done regarding the application of homomorphic cryptosystems in image processing. In particular, Ziad, et al. introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}. This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem.

However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security. Even though the authors claim that the operations in \textit{CryptoImg} are privacy-preserving, it is not clear whether the modified images are secure as well.
This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al. \cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem.

>>>>

Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\oplus$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}. Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}. These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.

However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}. Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data. While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010 ,sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.

@@

There has been work done regarding the application of homomorphic cryptosystems in image processing. In particular, Ziad, et al. introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}. This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem. Ziad, et al. also showed experimental results establishing the slow performance of image operations uner a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security. Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.

Furthermore, Ziad, et al. only presented a visual comparison and evaluation to establish the quality of the recovered images. We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.
This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al. \cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem which can be expressed using elementary number theory, without the use of lattices.
